### 2017-07-04 paper.tex
Tentative improvements of fig1
- make it included as pdf so it is not pixelized/rasterized (generated with inkscape + ghostscript cleaning)
- use a font that is closer (in style and size) to the paper's font
- add some space to breathe
- add crossroad sign (openclipart)
Fixing typos (for #32)

Despite the success of openness in software development and the curation of Wikipedia,
it is an uncommon approach in accademic settings.
Each year,
thousands of university lecturers teach subjects ranging from first year biology,
to graduate-level courses in Indian film.
Some use textbooks written by one or a few authors,
but beyond that,
they develop and maintain their course materials in isolation.
This is curious given that research depends critically on sharing,
and that most researchers complain about how much time teaching takes away from research,
but the sociology and pscyhology behind this blind spot are out of the scope of this paper.

@@

All open education projects satisfy the first criterion by definition,
but few satisfy the second.
While their lessons are occasionally updated by a small team
(as happens when a new edition of a book is edited and published),
this is not the same as continuous improvement by a large community of contributors.
The ten simple rules that follow summarize what we have learned about doing that.

@@

Finally,
working in the open can be great,
but can also unintentionally suppress voices.
Programming Historian makes an ombudsperson is available for private chats and facilitation
to ensure that no one is excluded.

@@

%%%%% Figure  dissociation
\begin{figure}[ht]  % h = here, t = top, b = bottom, p = float
\includegraphics[width=\linewidth]{figure1}
\caption{Graphical abstract of 10 simple rules for collaborative lesson development}
\label{figure1}
\end{figure}
%

>>>>

Despite the success of openness in software development and the curation of Wikipedia,
it is an uncommon approach in academic settings.
Each year,
thousands of university lecturers teach subjects ranging from first year biology,
to graduate-level courses in Indian film.
Some use textbooks written by one or a few authors,
but beyond that,
they develop and maintain their course materials in isolation.
This is curious given that research depends critically on sharing,
and that most researchers complain about how much time teaching takes away from research,
but the sociology and psychology behind this blind spot are out of the scope of this paper.

@@

All open education projects satisfy the first criterion by definition,
but few satisfy the second.
While their lessons are occasionally updated by a small team
(as happens when a new edition of a book is edited and published),
this is not the same as continuous improvement by a large community of contributors.
The ten simple rules that follow summarize what we have learned about doing that
as maintainers, editors, and reviewers of lessons used by tens of thousands of people (Fig. 1, 2).

@@

Finally,
working in the open can be great,
but can also unintentionally suppress voices.
Programming Historian makes an ombudsperson available for private chats and facilitation
to ensure that no one is excluded.

@@

%%%%% Figure  dissociation
\begin{figure}[ht]  % h = here, t = top, b = bottom, p = float
\includegraphics[width=\linewidth]{figure1}
\caption{Graphical abstract of 10 simple rules for collaborative lesson development}
\label{figure1}
\end{figure}

%%%%% Figure  dissociation
\begin{figure}[ht]  % h = here, t = top, b = bottom, p = float
\includegraphics[width=\linewidth]{figure2}
\caption{Collaborative open lesson development}
\label{figure2}
\end{figure}
